---
title: "FPEM"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn=-1)
```



## Table of Contents
1. [Introduction](#intro)
2. [Run models](#run)
3. [Post-process](#post-process)
4. [Plot model results](#plot)
  
## <a name="intro"></a>
## Introduction
This package is the one country implementation of FPEM. It uses higher level parameters estimated in FPEMglobal. The package can be installed by cloning and using `devtools::install()`. The source code for vignettes can be found in [/vignettes](https://github.com/FPcounts/FPEMcountry/tree/master/vignettes). Knitted versions of vignettes can be found in [/docs](https://github.com/FPcounts/FPEMcountry/tree/master/docs). The directory [/design](https://github.com/FPcounts/FPEM/tree/master/design) contains technical details about the design of this project for package maintainers and contributors. Below is a brief introduction.

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FPEMcountry)
library(ggplot2)
library(grid)
library(gridExtra)
devtools::load_all()
```
## <a name="run"></a>
## Run models
`do_1country_run` is a wrapper function to run the family planning estimation model for a country of interest for either married or unmarried women. When a survey file is not provided (as in this example) the function uses default data from `contraceptive_use`. The user may also supply optional services statistics. See `??service_stats` for required service statistic data format. See `??do_1country_run` for all possible inputs to this wrapper function. If you wish to obtain results for all women `posterior_samples_all_women` can be used after completing a run for married women and a run for unmarried women. See  [FPEM/vignettes](https://github.com/FPcounts/FPEMcountry/vignettes) for more details
```{r}
div <- 68 
fpem_one_country_autosave(
  runname = paste0(div),
  is_in_union = "ALL",
  service_stats = FALSE,
  division_numeric_code = div,
  first_year = 1975,
  last_year = 2030
)
```

## <a name="post-process"></a>
## Process the samples
`fpem_calculate_results` returns point-estimates for several indicators in long-format.
```{r}
fpem_get_results_autosave(
  runname = paste0(div)
)
```
## <a name="plot"></a>
## Plot the results
`fpem_plot_country_results` plots the results of the model againts the observations. Choose any indicators returned from `fpem_calculate_results`
```{r}

indicators <- c(
    "unmet_need_any",
    "contraceptive_use_modern",
    "contraceptive_use_traditional",
    "contraceptive_use_any"
    )

fpem_get_plots_autosave(
  runname = paste0(div),
  indicators = indicators,
  compare_to_global = TRUE
  )


# gridExtra::grid.arrange(grobs=plots[1:length(indicators)],
#                  ncol=2,
#                  top="In-union women")
```