---
title: "FPEM"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
# knitr::opts_knit$get("root.dir")  # alternative to the previous line
# the default autosave location will depend on this being setup
options(warn=-1)
```



## Table of Contents
1. [Introduction](#intro)
2. [Run models](#run)
3. [Post-process](#post-process)
4. [Plot model results](#plot)
  
## <a name="intro"></a>
## Introduction
This package is the one country implementation of FPEM. It uses higher level parameters estimated in FPEMglobal. The package can be installed by cloning and using `devtools::install()`. The source code for vignettes can be found in [/vignettes](https://github.com/FPcounts/FPEMcountry/tree/master/vignettes). The directory [/design](https://github.com/FPcounts/FPEM/tree/master/design) contains technical details about the design of this project for package maintainers and contributors. Below is a brief introduction.

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FPEMcountry)
devtools::load_all()
```
## <a name="run"></a>
## Run models
`fpem_one_country` is a generic wrapper function to run the family planning estimation model for a country of interest. The wrapper functions ending in `_autosave` such as `fpem_one_country_autosave` save the output and name the files using the runname argument. We will use the division code for Bolivia here as the runname.

When a survey file is not provided (as in this example) the function uses default data from `contraceptive_use`. The user may also supply optional services statistics. See `??service_stats` for required service statistic data format. See `??do_1country_run` for all possible inputs to this wrapper function. If you wish to obtain results for all women `posterior_samples_all_women` can be used after completing a run for married women and a run for unmarried women. See  [FPEM/vignettes](https://github.com/FPcounts/FPEMcountry/vignettes) for more details
```{r}
div <- 64
runlist <- fpem_one_country(
  is_in_union = "Y",
  service_stats = FALSE,
  division_numeric_code = div,
  first_year = 1970,
  last_year = 2030,
  diagnostic = TRUE,
  params_to_save = c(
    "mod.ct",
    "unmet.ct",
    "trad.ct",
    "mu.in",
    "logitratio.yunmet.hat.i",
    "pmax.c",
    "logitpmax.c",
    "logitRmax.c",
    "Rmax.c",
    "logitomega.c",
    "omega.c",
    "Romega.c",
    "logitRomega.c",
    "s.ct",
    "setlevel.c",
    "P.ct",
    "RT.c",
    "unmet.intercept.c"
  ),
  nchains = 6,
  niter = 5000,
  nburnin = 1000
)

```

## <a name="post-process"></a>
## Process the samples
`fpem_get_results` returns point-estimates for several indicators in long-format.
```{r}
results <- fpem_results(
  run
)
```
## <a name="plot"></a>
## Plot the results
`fpem_get_plots` plots the results of the model against the observations. Choose any indicators returned from `fpem_calculate_results`
```{r}
indicators <- c(
    "unmet_need_any",
    "contraceptive_use_modern",
    "contraceptive_use_traditional",
    "contraceptive_use_any"
    )

fpem_plot(
  runlist,
  results,
  indicators = indicators,
  compare_to_global = TRUE
  )
```


```{r}
mod <- runlist$run$mod
summ <- MCMCvis::MCMCsummary(mod)
temp <- summ[which(summ$Rhat > 1),]
rownames(temp)[1]
write.table(this, "this.txt")
bugs <- jagsout$BUGSoutput
max(bugs$summary[,"Rhat"])
bugs$summary[bugs$summary[,"Rhat"]>1.1,]
MCMCvis::MCMCtrace(jagsout,
          params = "all",
                 ISB = FALSE,
                 pdf = TRUE,
                 # prior = pr,
                 post_zm = TRUE,
          open_pdf = FALSE,
          Rhat = TRUE,
          filename = "output/mcmctrace.pdf")
          #wd = getwd())

```