---
title: "Estimating family planning indicators for married women"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
# knitr::opts_knit$get("root.dir")  # alternative to the previous line
# the default autosave location will depend on this being setup
options(warn=-1)
```


```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FPEMcountry)
devtools::load_all()
```

1. [Fit a one country model](#fit) `fit_fp_c`
2. [Calculate point estimates for indicators](#results) `calc_fp_c`
3. [Plot the  point estimates against the survey data](#plot) `plot_fp_c`

## <a name="fit"></a>
## 1. Fit a one country model

Call `fit_fp_c`  to fit the one-country family planning estimation model. The primary input to `fit_fp_c` is country-level survey data of contraceptive use aggregates. By default UNPD contraceptive use aggregates and filters the data based on country code and union status (See `??contraceptive_use` for UNPD contraceptive use aggregate data). Users may supply their own contraceptive use aggregate data. UNPD country codes, known as division numeric codes, are found in the package dataset called `divisions`. There are two versions of this model, one for in-union and another for not-in-union women which are specified with the argument `is_in_union` denoted `"Y"` and `"N"` respectively. Lastly, specify the years of estimates to be returned. Note: These arguments will not filter the supplied survey data. All years of available survey data will be used.
```{r}
fit <- fit_fp_c(
  division_numeric_code = 4,
  is_in_union = "Y",
  first_year = 1970,
  last_year = 2030
)
```


## <a name="results"></a>
## 2. Calculate point estimates for indicators
Calculate point estimates for family planning indicators with the function `calc_fp_c`. Simply supply the fit object from `fit_fp_c`. By default the function uses UNPD package data (See `??population_counts`). Users may supply their own population count data (See `??calc_fp_c`).
```{r}
results <- calc_fp_c(fit)
```

A set of results here consist of the following family planning indicators
```{r}
results$Y %>% names
```

The point estimates for each indicator are long-format tibbles. Let's take a look at the tibble for the indicator `contraceptive_use_modern`
```{r}
results$Y$contraceptive_use_modern
```


## <a name="plot"></a>
## 3. Plot estimates and survey data
FPEMcountry also includes a function named `plot_fp_c` to plot the calculated point estimates against the survey data. The arguments to this function are, the fit object from step 1, the results from step 2, and a vector of indicator names. The vector of indicator names corresponds to the names which appear in the results from step 2.
```{r}
plot_fp_c(
  fit,
  results,
  indicators = c(
    "unmet_need_any",
    "contraceptive_use_modern",
    "contraceptive_use_traditional",
    "contraceptive_use_any"
    )
  )
```
