---
title: "all country"
author: "Gregory Guranich"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{all country}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_chunk$set(echo = TRUE)
library(FPEMcountry)
devtools::load_all()
```

## Introduction
In this vignette we will fit FPET to multiple countries and aggregate the samples to obtain results for aggregate levels.
## Table of contents
1. [Fit models](#fit)
2. [Aggregate](#aggregate)
3. [Calculate results](#results)
  
## <a name="fit"></a>
## Fit models
Let’s task ourselves with obtaining results for each sub-region within Africa.
```{r}
divisions %>%
  dplyr::filter(name_region == "Africa") %>%
  dplyr::select(sub_region_numeric_code, name_sub_region) %>%
  unique()
```
First, we need fits for all countries in Africa. Start by constructing a list of country codes
```{r}
divs <- divisions %>%
  dplyr::filter(name_region == "Africa") %>%
  dplyr::filter(division_numeric_code %in% contraceptive_use$division_numeric_code) %>% # Filtering on the countries available in `contraceptive_use` because we are using this package data
  dplyr::pull(division_numeric_code) %>%
  as.list() 
```

Next, map the country codes to the function `fpet_fit_model’.
```{r}
first_year <- 1970
last_year <- 2030
union <- "Y"
fits <- purrr::pmap(list(division_numeric_code = divs, 
                         is_in_union = union,
                         first_year = first_year, 
                         last_year = last_year
                         ), 
                    fpet_fit_model)
```

## <a name="aggregate"></a>
## Aggregate
Within out list of fits we have more complex lists. We only need the samples from these fits. This function plucks the posterior samples and combines each array of samples along index 1 making one large array. The first index of this large array corresponds to the country of the samples. Use dimnames() on the resulting list to see how to index a country. This is the identical format of a posterior samples array from FPEMglobal.
```{r}
combined_samples <- combine_samples_from_fits(fits, divs)
```

To aggregate these samples we need to construct two tibbles. First, create a tibble with the aggregation level and corresponding division codes. The aggregation level column must be named division_level and contain division codes. In this example we will obtain aggregate results for all sub-regions in Africa. Everything we need for our division level column is in the column sub_region_numeric_code of the data set division.
```{r}
division_level_data <- divisions %>%
   dplyr::mutate(division_level = sub_region_numeric_code)%>%
   dplyr::select(division_numeric_code, division_level) %>% 
   dplyr::filter(division_numeric_code %in% divs)
division_level_data
```

Lastly, we need the population counts for these countries within the specified years.
```{r}
population_data <- population_counts %>%
  dplyr::filter(division_numeric_code %in% divs) %>%
  dplyr::filter(is_in_union == union) %>%
  dplyr::filter(mid_year >= first_year) %>%
  dplyr::filter(mid_year <= last_year) 
population_data
```
Now supply these two tibbles of data and the large array of posterior samples to the function fpem_aggregate. This function returns a named list of aggregated samples.
```{r}
posterior_samples_list <- fpem_aggregate(division_level_data, 
                                         population_data, 
                                         posterior_samples =  combined_samples)
names(posterior_samples_list)
```

## <a name="results"></a>
## Calculate results
We can map the list of samples to fpem_calculate_results to obtain results for each sub-region
```{r}
results_list <- purrr::pmap(list(posterior_samples = posterior_samples_list,
                            country_population_counts = list(population_data), #need to wrap any complex inputs in another list()
                            first_year = first_year),
                       fpem_calculate_results)
results_list$`912`$contraceptive_use_modern
```


